# Missing values 

## load data & preprocess data
 
- replace -1, Unknown/ Non-Applicable to NA 
- convert 'Salary Estimate' to col: low_salary, high_salary, avg_salary
- convert 'employee' to col: lower_bound_employee, upper_bound_employee, avg_employee

```{r echo=FALSE}
# Basics
if(!require(dplyr)) install.packages("dplyr")
if(!require(tibble)) install.packages("tibble")
if(!require(tidyr)) install.packages("tidyr")
if(!require(ggplot2)) install.packages("ggplot2")
if(!require(forcats)) install.packages("forcats")
if(!require(patchwork)) install.packages("patchwork")
if(!require(scales)) install.packages("scales")
if(!require(readr)) install.packages("readr")
if(!require(ggthemes)) install.packages("ggthemes")
if(!require(ggrepel)) install.packages("ggrepel")
if(!require(GGally)) install.packages("GGally")
if(!require(plotly)) install.packages("plotly")
if(!require(forcats)) install.packages("forcats")
if(!require(stringr)) install.packages("stringr")

if(!require(ggpubr)) install.packages("ggpubr")
if(!require(PupillometryR)) install.packages("PupillometryR")
if(!require(ggridges)) install.packages("ggridges")
if(!require(RColorBrewer)) install.packages("RColorBrewer")
if(!require(magrittr)) install.packages("magrittr") # allow %<>%

if(!require(vcd)) install.packages("vcd")
if(!require(d3r)) install.packages("d3r")
if(!require(ggalluvial)) install.packages("ggalluvial")
if(!require(parcoords)) install.packages("parcoords")

# pair plot
if(!require(gridGraphics)) install.packages("gridGraphics")
if(!require(gridExtra)) install.packages("gridExtra")

library("data.table")
library(mi)
```





```{r echo=FALSE}
ds_data = load("cleaned.RData")
head(ds_data)
View(ds_data)
```

## missing value by column:

```{r echo=FALSE}
colSums(is.na(ds_data)) %>%
  sort(decreasing = TRUE)
```
the dataset we have has missing data. Their values are NA, -1, Unknown and NOn-Applicable. We change all of them into NA to make the dataset more clear and concise. 
Then we converted “Salary Estimate” to columns “low_salary”, “high_salary”, and “avg_salary”. 
Then we converted “Emplyee” to columns “lower_bound_employee”, “high_bound_employee”, “avg_bound_employee”. 


## choose first ten company 

```{r echo=FALSE, fig.width = 13}
n_row = nrow(ds_data)
variables = colnames(ds_data)

ds_data %>% 
  slice(1:10) %>%
  mutate_all( as.character) %>%
  relocate(`Company Name`, 1) %>%
  pivot_longer(2:ncol(.)) %>%
  mutate(missing = ifelse(is.na(value), T, F)) %>%

ggplot() +
  geom_tile(aes(x=name,
                y=`Company Name`,
                fill=factor(missing))) + 
  labs(x = 'variable', y = 'company')+
  scale_fill_manual(values = c("grey60", alpha( "cornflowerblue", 0.6))) +
  scale_alpha_manual(values = c(0.5, 0.9)) +
  theme(axis.text.x = element_text(angle = 20,hjust = 0.95,vjust = 0.95))
```
For each columns, their number of missions values are show below. As we can see from the form, most of the values under “easy apply” and “competitor” labels are missing. That means we should avoid to investigate the relation of salary and these two features. 
Among all features, “Sectors”, “Industry”, and “number of employees” are least missing values. We want to investigate relations of these features and salary level. 


## use mi library draw heatmap and check missing value

```{r echo=TRUE, fig.height=6}
x <- mi::missing_data.frame(ds_data %>% as.data.frame())
image(x)
```

show patterns of missing value 
```{r}
levels(x@patterns)
```

```{r echo=FALSE}
summary(x@patterns)
```

```{r}
missing_value_plot <- function(df, showcount=TRUE){
  
  missing_patterns <- data.frame(is.na(df)) %>%
  group_by_all() %>%
  count(name = "count", sort = TRUE) %>%
  ungroup()
  n_row =  nrow(df)
  colname = colnames(df)

  up_table <- missing_patterns %>% 
      pivot_longer(-c(count), 
                   names_to = "var",
                   values_to = "missing") %>% 
      mutate(temp = missing * count) %>%
      group_by(var) %>%
      summarise(total_row = sum(temp)) %>% 
      arrange(-total_row) %>% 
      mutate(percent_row = total_row/n_row*100,var = fct_inorder(var))
  
  if(showcount){
    up_table %>%
    ggplot(aes(x = var ,y = total_row))+
    geom_col(show.legend = FALSE,fill="#4D65D0")+
    labs(x="",y="num rows missing") +
    scale_y_continuous(expand = c(0,0))+
    theme(axis.text.x = element_text(angle = 20,hjust = 0.95,vjust = 0.95))  -> p1
    
  }else{
    up_table %>%
    ggplot(aes(x = var ,y = percent_row))+
    geom_col(show.legend = FALSE,fill="#4D65D0")+
    labs(x="",y="% rows missing") +
    scale_y_continuous(expand = c(0,0),limits = c(0,100))+
    theme(axis.text.x = element_text(angle = 20,hjust = 0.95,vjust = 0.95)) -> p1
  }

  var_seq = levels(fct_inorder(up_table$var))
  
  missing_patterns %>% 
      arrange(-count) %>%
      mutate(index = factor(1:n()),
             percent_pat = count/n_row*100) ->  temp_1
      temp_1 %>% select_at(var_seq) %>%
      apply(1, sum) -> missing_sum
  
      temp_1 %>%
      mutate(missing_sum = missing_sum,
           complete_cases = ifelse(missing_sum == 0, T,F))   %>% 
      select(c(index,percent_pat,count,complete_cases)) -> right_table
  
  if(showcount){
    right_table %>%
    ggplot(aes(x = count,y = fct_rev(index),fill=complete_cases))+
    geom_col(show.legend = FALSE)+
    scale_fill_manual(values = c("#4D65D0", "#2A22FF")) +
    labs(x="row count",y="")+
    scale_x_continuous(expand = c(0,0)) +
    theme(axis.text.x = element_text(angle = 20,hjust = 0.95,vjust = 0.95))-> p2
    
  }else{
    right_table %>%
    ggplot(aes(x = percent_pat,y = fct_rev(index),fill=complete_cases))+
    geom_col(show.legend = FALSE)+
    scale_fill_manual(values = c("#4D65D0", "#2A22FF")) +
    labs(x="% rows",y="")+
    scale_x_continuous(expand = c(0,0),limits = c(0,100)) +
    theme(axis.text.x = element_text(angle = 20,hjust = 0.95,vjust = 0.95)) -> p2 }
    
  central_table <- missing_patterns %>% 
      arrange(-count) %>%
      select_at(var_seq) %>% 
      mutate(index = factor(1:n())) ->  temp_2
      temp_2 %>% select_at(var_seq) %>%
      apply(1, sum) -> missing_sum_1
  
    central_table <- temp_2 %>%
      mutate(missing_sum_1 = missing_sum_1,
           complete_cases = ifelse(missing_sum_1 == 0, T,F))   %>% 
      pivot_longer(-c(index,complete_cases,missing_sum_1),names_to = "var", values_to = "missing") %>%
      rename(feature = var) %>%
      mutate(feature = factor(feature, levels = var_seq))
 
  n = ceiling((length(var_seq))/2)

  tibble(index = central_table %>% filter(complete_cases) %>% distinct(index) %>% pull(index),
         feature = var_seq[n],
         label = "complete cases") -> text
  
  
  central_table %>% 
    
    ggplot() +
    geom_tile(aes(x=feature,y=fct_rev(index),fill=factor(missing),alpha=complete_cases),
              color = "white",show.legend = FALSE) + 
    geom_text(data = text,
              aes(x = feature, 
                  y = index,
                  label = label),
              size = 6,
              color = "black",
              na.rm = TRUE)  +
    labs(x = 'variable', y = 'missing pattern')+
    scale_fill_manual(values = c("grey40", "purple")) +
    scale_alpha_manual(values = c(0.5, 0.9)) +
    theme(axis.text.x = element_text(angle = 20,hjust = 0.95,vjust = 0.95))-> p3
    
 layout<- "111111144
  111111144
  333333322
  333333322
  333333322
  333333322
  333333322
  333333322
  333333322"
  print(p1+p2+p3 + plot_layout(design = layout))
}

```

## draw the missing pattern plot using the function from homework
```{r echo=FALSE, fig.width=15,fig.height=13}
missing_value_plot(ds_data,showcount = F)
```


```{r echo=FALSE, fig.width=15,fig.height=13}
missing_value_plot(ds_data,showcount = T)
```

The most frequent missing pattern is the pattern where Easy.apply and Competitors are both missing, while the other variables are not. Moreover, Easy.apply and Competitors are more likely to be missing in the dataset than the other variables. 

While other values are missing, the values of Company.name, index, Job.Description, Job.Title, Location, Salary.Estimate, and X are all presenting in the dataset. 

The features Industry and Sector seem to be missing at the same time. 

The feature Founded seems to be an independent feature, its representing doesn't effect other feature’s status. 

Complete cases only appears less than 100 rows while there are more than 2000 rows of data in the set.