--- 
title: "DSSalaryAnalysis"
author: "Huaizhi Ge, Huanyu Jiang and Binghong Yu"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
---
```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```



# Introduction

We chosed this topic because data science is our shared major. Over the last ten years, data science has progressed considerably. Data science is an enthralling, lucrative, and rapidly expanding discipline. Data scientists organize and analyze enormous amounts of information, look for trends, and make predictions. Data science majored students are required in nearly every field, including business, finance, science, health, and government. As students who are looking for a position in job market, the first thing concerning us is the salary of a job position. As a data science student, we are interested in learning the salary patterns in different data science positions. We do so with the techniques we learned in class. 

<!--chapter:end:index.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Data sources

data link: https://github.com/picklesueat/data_jobs_data


The data was collected from Glassdoor, an anonymous review service for current and past employees in the United States. On Glassdoor, users may anonymously post and view salaries, as well as search for and apply for jobs. Binghong Yu was responsible for collecting the data. We tried to scrap the website. however the api provided by Glassdoor was taken down and no longer available to the public. As a result, we failed to scrap the website. But we found the scraped data from GitHub, and downloaded it. 


The dataset is created by picklesueat from Glassdoor. This repo contains four files, including: BusinessAnalyst.csv (4092x15), DataAnalyst.csv (5631x15), DataEngineer.csv (2528x15), and DataScientist.csv (3909x15).Each gives information about a branch of data related jobs. For each of them, there are 15 features: 'Job Title', 'Salary Estimate', 'Job Description', 'Rating', 'Company Name', Location', 'Headquarters', 'Size', 'Founded', 'Type of ownership', 'Industry', Sector', 'Revenue', 'Competitors', 'Easy Apply’.

There were a few problems with the raw dataset, and we cleaned it so that it could giver much more clear information for the further analysis. 

First of all, some of the data were classified as multiple job types, but we want 1-1 classsification. Therefore, we relabeled the data based on its job title and job description. 

Then, due to scraping errors, company names are followed by its rating. We seperated the names and its rating. 

Secondly, the value of salary feature contains words “GlassDoor estimated”. We only want the actual number of salary, so we deleted the words contained in the salary column and replaced "k", representing thousands, as "1,000".

Thirdly, we modified job titles. For example, some of the job titles contains key words "Jr" and "Sr" while others uses "Junior" and "Senior". To make the data make more sense, we modified them to have the same representation. We made them follow a certain pattern to give a more clear information. 

Finally, we modified number of employer. For some of the data, number of employers was represented by a range, while others were represented by a specific number. This made the analysis more complicated. We take mean of the range and let the mean to be the new value of this feature. 

<!--chapter:end:02-data.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Data transformation

<!--chapter:end:03-cleaning.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Missing values 

## load data & preprocess data
 
- replace -1, Unknown/ Non-Applicable to NA 
- convert 'Salary Estimate' to col: low_salary, high_salary, avg_salary
- convert 'employee' to col: lower_bound_employee, upper_bound_employee, avg_employee

```{r echo=FALSE}
# Basics
if(!require(dplyr)) install.packages("dplyr")
if(!require(tibble)) install.packages("tibble")
if(!require(tidyr)) install.packages("tidyr")
if(!require(ggplot2)) install.packages("ggplot2")
if(!require(forcats)) install.packages("forcats")
if(!require(patchwork)) install.packages("patchwork")
if(!require(scales)) install.packages("scales")
if(!require(readr)) install.packages("readr")
if(!require(ggthemes)) install.packages("ggthemes")
if(!require(ggrepel)) install.packages("ggrepel")
if(!require(GGally)) install.packages("GGally")
if(!require(plotly)) install.packages("plotly")
if(!require(forcats)) install.packages("forcats")
if(!require(stringr)) install.packages("stringr")

if(!require(ggpubr)) install.packages("ggpubr")
if(!require(PupillometryR)) install.packages("PupillometryR")
if(!require(ggridges)) install.packages("ggridges")
if(!require(RColorBrewer)) install.packages("RColorBrewer")
if(!require(magrittr)) install.packages("magrittr") # allow %<>%

if(!require(vcd)) install.packages("vcd")
if(!require(d3r)) install.packages("d3r")
if(!require(ggalluvial)) install.packages("ggalluvial")
if(!require(parcoords)) install.packages("parcoords")

# pair plot
if(!require(gridGraphics)) install.packages("gridGraphics")
if(!require(gridExtra)) install.packages("gridExtra")

library("data.table")
library(mi)
```

```{r echo=FALSE}
ds_data = fread('data/DataScientist.csv') 
ds_data %>%
  select(3:ncol(.)) %>%
  mutate_all(~ifelse(. %in% c("NA", -1, "Unknown", "Unknown / Non-Applicable"), NA, .))   %>%
  as_tibble %>%
  separate(`Salary Estimate`, into = c("low","high"), sep = "-",remove = T) %>%
  mutate(low_salary = as.numeric(str_extract(low, "\\d+")),
         high_salary = as.numeric(str_extract(high, "\\d+")),
         avg_salary = (low_salary + high_salary) / 2)  %>% 

  separate(Size, into = c("low_ppl","high_ppl"), sep = "to", remove = T) %>% 
  mutate(lower_bound_employee = as.numeric(str_extract(low_ppl, "\\d+")),
         upper_bound_employee = as.numeric(str_extract(high_ppl, "\\d+")),
         avg_employee= case_when(
           !is.na(lower_bound_employee) & is.na(upper_bound_employee) ~ lower_bound_employee,
           T ~ (lower_bound_employee + upper_bound_employee) / 2)) ->ds_data
```



```{r echo=FALSE}
head(ds_data)

```

## missing value by column:

```{r echo=FALSE}
colSums(is.na(ds_data)) %>%
  sort(decreasing = TRUE)
```

## choose first ten company 

```{r echo=FALSE, fig.width = 13}
n_row = nrow(ds_data)
variables = colnames(ds_data)

ds_data %>% 
  slice(1:10) %>%
  mutate_all( as.character) %>%
  relocate(`Company Name`, 1) %>%
  pivot_longer(2:ncol(.)) %>%
  mutate(missing = ifelse(is.na(value), T, F)) %>%

ggplot() +
  geom_tile(aes(x=name,
                y=`Company Name`,
                fill=factor(missing))) + 
  labs(x = 'variable', y = 'company')+
  scale_fill_manual(values = c("grey60", alpha( "cornflowerblue", 0.6))) +
  scale_alpha_manual(values = c(0.5, 0.9)) +
  theme(axis.text.x = element_text(angle = 20,hjust = 0.95,vjust = 0.95))
```

## use mi library draw heatmap and check missing value

```{r echo=TRUE, fig.height=6}
x <- mi::missing_data.frame(ds_data %>% as.data.frame())
image(x)
```

show patterns of missing value 
```{r}
levels(x@patterns)
```

```{r echo=FALSE}
summary(x@patterns)
```

```{r}
missing_value_plot <- function(df, showcount=TRUE){
  
  missing_patterns <- data.frame(is.na(df)) %>%
  group_by_all() %>%
  count(name = "count", sort = TRUE) %>%
  ungroup()
  n_row =  nrow(df)
  colname = colnames(df)

  up_table <- missing_patterns %>% 
      pivot_longer(-c(count), 
                   names_to = "var",
                   values_to = "missing") %>% 
      mutate(temp = missing * count) %>%
      group_by(var) %>%
      summarise(total_row = sum(temp)) %>% 
      arrange(-total_row) %>% 
      mutate(percent_row = total_row/n_row*100,var = fct_inorder(var))
  
  if(showcount){
    up_table %>%
    ggplot(aes(x = var ,y = total_row))+
    geom_col(show.legend = FALSE,fill="#4D65D0")+
    labs(x="",y="num rows missing") +
    scale_y_continuous(expand = c(0,0))+
    theme(axis.text.x = element_text(angle = 20,hjust = 0.95,vjust = 0.95))  -> p1
    
  }else{
    up_table %>%
    ggplot(aes(x = var ,y = percent_row))+
    geom_col(show.legend = FALSE,fill="#4D65D0")+
    labs(x="",y="% rows missing") +
    scale_y_continuous(expand = c(0,0),limits = c(0,100))+
    theme(axis.text.x = element_text(angle = 20,hjust = 0.95,vjust = 0.95)) -> p1
  }

  var_seq = levels(fct_inorder(up_table$var))
  
  missing_patterns %>% 
      arrange(-count) %>%
      mutate(index = factor(1:n()),
             percent_pat = count/n_row*100) ->  temp_1
      temp_1 %>% select_at(var_seq) %>%
      apply(1, sum) -> missing_sum
  
      temp_1 %>%
      mutate(missing_sum = missing_sum,
           complete_cases = ifelse(missing_sum == 0, T,F))   %>% 
      select(c(index,percent_pat,count,complete_cases)) -> right_table
  
  if(showcount){
    right_table %>%
    ggplot(aes(x = count,y = fct_rev(index),fill=complete_cases))+
    geom_col(show.legend = FALSE)+
    scale_fill_manual(values = c("#4D65D0", "#2A22FF")) +
    labs(x="row count",y="")+
    scale_x_continuous(expand = c(0,0)) +
    theme(axis.text.x = element_text(angle = 20,hjust = 0.95,vjust = 0.95))-> p2
    
  }else{
    right_table %>%
    ggplot(aes(x = percent_pat,y = fct_rev(index),fill=complete_cases))+
    geom_col(show.legend = FALSE)+
    scale_fill_manual(values = c("#4D65D0", "#2A22FF")) +
    labs(x="% rows",y="")+
    scale_x_continuous(expand = c(0,0),limits = c(0,100)) +
    theme(axis.text.x = element_text(angle = 20,hjust = 0.95,vjust = 0.95)) -> p2 }
    
  central_table <- missing_patterns %>% 
      arrange(-count) %>%
      select_at(var_seq) %>% 
      mutate(index = factor(1:n())) ->  temp_2
      temp_2 %>% select_at(var_seq) %>%
      apply(1, sum) -> missing_sum_1
  
    central_table <- temp_2 %>%
      mutate(missing_sum_1 = missing_sum_1,
           complete_cases = ifelse(missing_sum_1 == 0, T,F))   %>% 
      pivot_longer(-c(index,complete_cases,missing_sum_1),names_to = "var", values_to = "missing") %>%
      rename(feature = var) %>%
      mutate(feature = factor(feature, levels = var_seq))
 
  n = ceiling((length(var_seq))/2)

  tibble(index = central_table %>% filter(complete_cases) %>% distinct(index) %>% pull(index),
         feature = var_seq[n],
         label = "complete cases") -> text
  
  
  central_table %>% 
    
    ggplot() +
    geom_tile(aes(x=feature,y=fct_rev(index),fill=factor(missing),alpha=complete_cases),
              color = "white",show.legend = FALSE) + 
    geom_text(data = text,
              aes(x = feature, 
                  y = index,
                  label = label),
              size = 6,
              color = "black",
              na.rm = TRUE)  +
    labs(x = 'variable', y = 'missing pattern')+
    scale_fill_manual(values = c("grey40", "purple")) +
    scale_alpha_manual(values = c(0.5, 0.9)) +
    theme(axis.text.x = element_text(angle = 20,hjust = 0.95,vjust = 0.95))-> p3
    
 layout<- "111111144
  111111144
  333333322
  333333322
  333333322
  333333322
  333333322
  333333322
  333333322"
  print(p1+p2+p3 + plot_layout(design = layout))
}

```

## draw the missing pattern plot using the function from homework
```{r echo=FALSE, fig.width=15,fig.height=13}
missing_value_plot(ds_data,showcount = F)
```


```{r echo=FALSE, fig.width=15,fig.height=13}
missing_value_plot(ds_data,showcount = T)
```

The most frequent missing pattern is the pattern where Easy.apply and Competitors are both missing, while the other variables are not. Moreover, Easy.apply and Competitors are more likely to be missing in the dataset than the other variables. 

While other values are missing, the values of Company.name, index, Job.Description, Job.Title, Location, Salary.Estimate, and X are all presenting in the dataset. 

The features Industry and Sector seem to be missing at the same time. 

The feature Founded seems to be an independent feature, its representing doesn't effect other feature’s status. 

Complete cases only appears less than 100 rows while there are more than 2000 rows of data in the set.

<!--chapter:end:04-missing.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Results

<!--chapter:end:05-results.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Interactive component



<!--chapter:end:06-interactive.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Conclusion


<!--chapter:end:07-conclusion.Rmd-->

